---
title: "Beerio Statistics"
date: "Updated: `r gsub(' 0', ' ', format(Sys.Date(), format='%b %d, %Y'))`"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(googlesheets4)
library(extrafont)
library(ggforce)
library(ggimage)
library(DT)
ttf_import("./fonts")
# font_import()
# Sys.setenv(R_GSCMD="C:/Program Files/gs/gs9.50/bin/gswin64c.exe")
loadfonts(device = "win")
#sheets_auth("cclanfear@gmail.com")
theme_mk8 <- function(){
  theme_minimal(base_size = 14) + 
    theme(title  = element_text(family = "Mario Kart F2"), 
          panel.grid.major.x = element_blank(), 
          panel.grid.minor.x = element_blank())
}
```

```{r punishment, include=FALSE}
shot_index <- c("one", "oh lawd two", "SAVE ME BABY JESUS THREE", "--ohhhh, body massage--four")
extract_punishment <-  function(x, type = "text"){ 
    if(x == "None"){
      return(NA_character_)
    } else {
      split_string <- x%>%
      str_split(",( )?") %>% 
      unlist()
      punish_count_df <- 
        tibble(take = str_remove_all(str_extract_all(split_string, "->( )?[A-Za-z]*"), "->( )?"),
               give = str_remove_all(str_extract_all(split_string, "[A-Za-z]*( )?->"), "( )?->")) %>%
          count(take, give)
    if (type =="text"){
        punish_count_df %>%
        mutate(take = ifelse(take==give, "himself", take)) %>%
          mutate(punishment_text = str_c(give, " gave ", shot_index[n], " to ", take)) %>%
          pull(punishment_text) %>%
          str_c(., collapse=", ") %>% 
        return()
    } else if (type == "punished"){
      punish_count_df %>%
           select(Punished=take, Shots=n) %>% return(.)
    } else if (type == "punisher"){
      punish_count_df %>%  mutate(give = ifelse(take==give, NA, give)) %>% select(Punisher=give, Shots=n) %>% return(.)
    }
}}
```

```{r processing, include=FALSE}
beerio_sheet_raw <- read_sheet("https://docs.google.com/spreadsheets/d/1V-7lY3NVqVGGEWL-jwwmjYcpLT8mJMN1MI11y-C3Bl0/", sheet = "Data")

beerio_data_temp <- beerio_sheet_raw %>%
  select(-contains("...")) %>%
  filter_all(any_vars(!is.na(.))) %>%
  fill(Date) %>%
  group_by(Date) %>%
  mutate(Day = str_replace(format(Date, "%b %e"), "  ", " ")) %>%
  mutate(Game = row_number()) %>%
  select(-Punishment) %>%
  pivot_longer(c(-Date, - Game, -Day), names_to = "Name", values_to = "Score") %>%
  ungroup()
```

```{r, include=FALSE}

# Need Date, Game, Name, Take, Give

punishment_df <- beerio_sheet_raw %>%
  select(-contains("...")) %>%
  filter_all(any_vars(!is.na(.))) %>%
  fill(Date) %>%
  group_by(Date) %>%
  mutate(Day = str_replace(format(Date, "%b %e"), "  ", " ")) %>%
  mutate(Game = row_number()) %>%
  ungroup() %>%
  select(Date, Game, Punishment) %>%
  filter(!is.na(Punishment)) %>%
  mutate(Punishment = str_split(Punishment, ",( )?")) %>%
  unnest(Punishment) %>%
  mutate(take = str_remove_all(str_extract_all(Punishment, "->( )?[A-Za-z]*"), "->( )?"),
         give = str_remove_all(str_extract_all(Punishment, "[A-Za-z]*( )?->"), "( )?->")) %>%
  mutate(give = ifelse(take==give, NA, give))

shots_take <- punishment_df %>%
  filter(!is.na(take)) %>%
  count(Date, Game, take) %>%
  rename(Name = take, Take = n)
shots_give <- punishment_df %>%
  filter(!is.na(give)) %>%
  count(Date, Game, give) %>%
  rename(Name = give, Give = n)
shots_df <- full_join(shots_take, shots_give)

beerio_data <- beerio_data_temp %>% left_join(shots_df)
```

```{r, include=FALSE}
last_players <- beerio_data %>%
  filter(Date ==  max(Date)) %>%
  filter(!is.na(Score)) %>%
  distinct(Name) %>% pull(Name)

if(length(last_players)==2){
  last_players_text <- paste(last_players, collapse = " and ")
} else {
  last_players_text <- paste(
    paste(last_players[-length(last_players)], collapse = ", "), ", and ",
    last_players[length(last_players)], sep="")
}

n_recent_games <- beerio_data %>%
  filter(Date ==  max(Date)) %>% pull(Game) %>% max()

winners <- beerio_data %>% 
  select(Date, Game, Name, Score) %>%
  filter(!is.na(Score)) %>%
  group_by(Date, Game) %>%
  mutate(Winner = ifelse(Score == max(Score), "Winner", "Not Winner")) %>%
  filter(Winner == "Winner") %>%
  mutate(n_winners = n()) %>%
  summarize(Winner = case_when(
    sum(n_winners) ==1 ~ first(Name),
    sum(n_winners) > 1 ~ "Tie"
  ))
```

This document tracks Beerio game statistics. The last tracked `r ifelse(n_recent_games > 1, "games were", "game was")` `r ifelse(n_recent_games==1, "one", n_recent_games)` `r ifelse(n_recent_games > 1, "games", "game")` played on `r str_replace(format(max(beerio_data$Date), "%A, %B %e, %Y"), "  ", " ")` by `r last_players_text`.

# All Game Data

This table contains scores and events for all logged games. It is searchable and sortable on all columns.

```{r, echo=FALSE, warning=FALSE, message=FALSE}

all_games <- beerio_sheet_raw %>%
  select(-contains("...")) %>%
  filter_all(any_vars(!is.na(.))) %>%
  fill(Date) %>%
  group_by(Date) %>%
  mutate(Game = row_number()) %>%
  arrange(desc(Date, Game)) %>%
  ungroup() %>%
  mutate(Date = str_replace(format(Date, "%A, %B %e, %Y"), "  ", " ")) %>%
  mutate(Punishment = ifelse(is.na(Punishment), "None", Punishment)) %>%
  mutate(Punishment = map_chr(Punishment, ~extract_punishment(., type = "text"))) %>%
  select(Date, Game, everything(), Punishment)
# datatable(all_games, options = list(pageLength = 10, scrollY=FALSE, paging=TRUE, info=TRUE), escape=FALSE, autoHideNavigation=TRUE, rownames=FALSE)

DT::datatable({
  all_games %>% mutate_all(~as.character(.)) %>% select(Date, Game, Chuck, Neil, Shawn, Steve, Punishment)
},
callback = JS("
  $.fn.dataTableExt.oSort['NumericOrBlank-asc'] = function(x,y) {
    var retVal;
        if( x === '' || $.isEmptyObject(x)) x = 1000;
    if( y === '' || $.isEmptyObject(y)) y = 1000;
    x = (x = parseFloat($.trim(x).replace(/,/g,''))) ? x : 0;
    y = (y = parseFloat($.trim(y).replace(/,/g,''))) ? y : 0;
    if (x==y) retVal= 0; 
    else retVal = (x>y) ? 1 : -1; 
    return retVal;
  };
  $.fn.dataTableExt.oSort['NumericOrBlank-desc'] = function(y,x) {
  var retVal;
  x = (x = parseFloat($.trim(x).replace(/,/g,''))) ? x : 0;
  y = (y = parseFloat($.trim(y).replace(/,/g,''))) ? y : 0;
  if (x==y) retVal= 0; 
  else retVal = (x>y) ? 1 : -1; 
  return retVal;
  };
  "),
options = list(
  autoWidth = TRUE,
  fillContainer = TRUE,
  pageLength = 10, paging=TRUE, info=TRUE, searching=TRUE, lengthChange=TRUE,
  aoColumnDefs = list(
    list(width = "45px", className = 'dt-center',  targets = c(1)),
    list(width = '45px',  bSortable = TRUE, sType = 'NumericOrBlank', className = 'dt-center', targets = c(2,3,4,5)),
    list(width = '250px', bSortable = TRUE, sType = 'NumericOrBlank', className = 'dt-center', targets = c(6)))
), escape=FALSE, autoHideNavigation=TRUE, rownames=FALSE, extensions = "Responsive")

```



# Descriptive Statistics

This table depicts overall Beerio statistics for all tracked players. Recent Average is calculated as the average score from the last date the player played.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
beerio_table <- beerio_data %>% 
  group_by(Name) %>% 
  summarize(`Games<br>Played`    = sum(!is.na(Score)), 
            `Overall<br>Average` = round(mean(Score, na.rm=T),1), 
            `Best<br>Score`      = max(Score, na.rm=T), 
            `Worst<br>Score`     = min(Score, na.rm=T),
            `Times<br>Punished`  = sum(Take, na.rm=T),
            `Times<br>Punisher`  = sum(Give, na.rm=T)) %>% 
  left_join(beerio_data %>% 
    group_by(Name) %>%
    filter(!is.na(Score)) %>%
    filter(Date==max(Date)) %>%
    summarize(`Recent<br>Average`=round(mean(Score),1))) %>%
  left_join(winners %>% 
              ungroup() %>% 
              filter(Winner != "Tie") %>% 
              count(Name = Winner) %>% 
              complete(Name = unique(beerio_data$Name), fill = list(n=0)) %>%
              rename(Victories = n)) %>%
  mutate(Name = case_when(
    Name == "Chuck" ~ "<img src = 'img/lightblueshyguy.png' height=20> Chuck",
    Name == "Neil" ~ "<img src = 'img/blackshyguy.png' height=20> Neil",
    Name == "Shawn" ~ "<img src = 'img/catpeach.png' height=20> Shawn",
    Name == "Steve" ~ "<img src = 'img/toadette.png' height=20> Steve",
    Name == "Korl" ~ "<img src = 'img/lakitu.png' height=20> Korl",
    Name == "Chad" ~ "<img src = 'img/donkeykong.png' height=20> Chad",
    TRUE ~ paste0(Name, " <img src = 'img/questionmark.png' height=20>")
  )) %>%
  mutate(`Win<br>Percentage` = round(Victories/`Games<br>Played`,2)) %>%
  select(Name, `Games<br>Played`,Victories, `Win<br>Percentage`, `Overall<br>Average`, `Recent<br>Average`, `Best<br>Score`, `Worst<br>Score`, `Times<br>Punished`, `Times<br>Punisher`)
  datatable(beerio_table, 
            options = list(pageLength = 10, searching=FALSE, lengthChange=FALSE, paging=FALSE, info=FALSE,
                           columnDefs = 
                             list(
                               list(className = 'dt-center',  targets = c(1,2,3,4,5,6,7,8,9))
                               )
                           ), 
            escape=FALSE, autoHideNavigation=TRUE, rownames=FALSE, extensions = "Responsive")
```

# Figures

The first figure depicts Beerio scores over games in each day. Punishments are indicated by a blue shell. Days with only one game are excluded.

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=10, fig.align='center', dev="png", dpi = 300}
beerio_data %>%
  group_by(Date) %>%
  filter(max(Game) > 1) %>%
  ungroup() %>%
  arrange(desc(Date)) %>%
  mutate(Day = fct_reorder(Day, Date, .desc=T)) %>%
  ggplot(aes(x = Game, y = Score, group = Name, color = Name)) + 
  facet_wrap(~ Day, scales = "free_x") + 
  geom_line(size = 2) +
  geom_image(data = beerio_data %>% filter(!is.na(Take)) %>% mutate(Day = fct_reorder(Day, Date, .desc=T)) %>% mutate(Image = "img/blueshell.png"), 
             aes(x = Game, y = Score, image = Image), 
             size = .125, inherit.aes = FALSE) + 
  ylab("") + scale_color_discrete("") +
  scale_x_continuous(breaks = function(x) unique(floor(pretty(seq(0, (max(x) + 1) * 1.1))))) +
  ylim(0, NA) +
  ggtitle("Beerio Scores", subtitle = "Over the course of evenings") +
  theme_mk8() + theme(legend.position="bottom")

score_text <- broom::tidy(lm(Score ~ Game + Name, data = beerio_data), conf.int=TRUE) %>% 
  select(term, estimate, conf.low, conf.high) %>% filter(term == "Game") %>%
  mutate_if(is.numeric, ~ round(.,2)) %>%
  mutate(text_value = paste0(estimate, " (95% CI: ", conf.low, ", ",conf.high, ")")) %>% 
  pull(text_value)

```

The next plot pools the data across evenings to show the change in average score for each player as the evening wears on. Points indicate scores for each match, jittered horizontally to reduce overplotting. Lines are simple linear regressions of score on game number. Note the trend is relatively similar across players. Each additional game is associated with a score difference of `r score_text`. 

```{r echo=FALSE, warning=FALSE, message=FALSE, fig.width=10, fig.align='center', dev="png", dpi = 300}
legend_data <- tibble(x = max(beerio_data$Game, na.rm=T)*0.9,
                      y = max(beerio_data$Score, na.rm=T)*c(1, 0.90),
                      image = c("img/star.png","img/bomb.png"),
                      text = c("Gave Shot", "Took Shot"))
ggplot(beerio_data, aes(x = Game, y = Score)) + 
  geom_smooth(method="lm", aes(color=Name, fill =Name), size = 2, se=FALSE) + 
  geom_point(data = beerio_data %>%  
               filter(is.na(Give) & is.na(Take)), aes(fill=Name), size =3, shape  = 21, color = "black", position = position_jitter(height=0, width=0.1)) + 
  theme_mk8() + ylab("") + scale_fill_discrete("") +
  scale_color_discrete("") +
  geom_point(data = beerio_data %>%  
               filter(!is.na(Take) | !is.na(Give)) %>% 
               select(Name, Game, Score, Give, Take), 
             aes(x = Game, y = Score, color = Name), 
             size = 12, inherit.aes = FALSE, alpha = 0.5) +
  geom_image(data = beerio_data %>%  
               filter(!is.na(Take) | !is.na(Give)) %>%
               mutate(Image = case_when(
                 !is.na(Take) ~ "img/bomb.png",
                 !is.na(Give) ~ "img/star.png")) %>% 
               select(Game, Score, Image), 
             aes(x = Game, y = Score, image = Image), 
             size = .05, inherit.aes = FALSE) +
  geom_image(data=legend_data, aes(x=x, y=y, image=image), inherit.aes=FALSE) +
  geom_text(data=legend_data, aes(x=x, y=y, label = text), hjust = 0, nudge_x = 0.25, inherit.aes=FALSE) +
  ggtitle("Beerio Score Over Games", subtitle = "Regressed on game number") + 
  coord_cartesian(ylim = c(0, max(beerio_data$Score+3))) +
  theme(legend.position = "bottom")
```

The next plot depicts overall score distributions for each player as a violin--a symmetrical density plot. Wider cross-sections indicate more games with scores in that range. Points indicate scores for each match, jittered horizontally to reduce overplotting. The line inside the violin denotes the median score.

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=10, fig.align='center', dev="png", dpi = 300}

legend_data <- tibble(x = length(unique(beerio_data$Name))*c(1.05, 0.95),
                      y = max(beerio_data$Score, na.rm=T)*0.90,
                      image = c("img/star.png","img/bomb.png"),
                      text = c("Gave Shot", "Took Shot"))
                      
beerio_data %>%
  ggplot(aes( y = Name, x = Score, fill = Name)) + 
  geom_violin(show.legend=FALSE, draw_quantiles = c(0.5)) + 
  geom_point(data = beerio_data %>% filter(is.na(Give) & is.na(Take)), 
             aes(y = Name, x = Score),  alpha = 0.5, size = 3, 
             position = position_jitter(height = 0.08, width=0), inherit.aes = FALSE) +
  geom_image(data = beerio_data %>%  
               filter(!is.na(Give) | !is.na(Take)) %>%
               mutate(Image = case_when(
                 !is.na(Take) ~ "img/bomb.png",
                 !is.na(Give) ~ "img/star.png")) %>% 
               select(Game, Score, Image, Name), 
             aes(y = Name, x = Score, image = Image), position = position_jitter(height = 0.08, width=0), 
             size = .05, inherit.aes = FALSE) +
  geom_image(data=legend_data, aes(y=x, x=y, image=image), inherit.aes=FALSE) +
  geom_text(data=legend_data, aes(y=x, x=y, label = text), hjust = 0, nudge_x = 1, inherit.aes=FALSE) +
  scale_color_manual("Shots", values = c("No Shot" = "black", "Give" = "white", "Take" = "red")) +
  xlab("") + 
  ylab("") +
  scale_y_discrete(limits = rev(c("Chuck", "Neil", "Shawn", "Steve"))) +
  coord_cartesian(xlim = c(min(beerio_data$Score-3), max(beerio_data$Score+3))) +
  theme_mk8() + 
  theme(legend.position = "bottom", legend.key = element_rect(fill = "gray70", color = NA)) + 
  ggtitle("Individual Score Distributions")
```

```{r, echo=FALSE}
# beerio_data %>%
#   ggplot(aes( x = Name, y = Score, fill = Name)) + 
#   geom_violin(show.legend=FALSE) + 
#   geom_point(data = beerio_data %>% filter(Give_and_Take == "No Shot"), 
#              aes(x = Name, y = Score),  alpha = 0.5, size = 3, 
#              position = position_jitter(width = 0.08, height=0), inherit.aes = FALSE) +
#   geom_image(data = beerio_data %>%  
#                filter(!is.na(Punished)) %>%
#                mutate(Image = case_when(
#                  Give_and_Take == "Take" ~ "img/bomb.png",
#                  Give_and_Take == "Give" ~ "img/star.png")) %>% 
#                select(Name, Score, Image), 
#              aes(x = Name, y = Score, image = Image), position = position_jitter(width = 0.08, height=0), 
#              size = .05, inherit.aes = FALSE) +
#   geom_image(data=legend_data, aes(x=x, y=y, image=image), inherit.aes=FALSE) +
#   geom_text(data=legend_data, aes(x=x, y=y, label = text), hjust = 0, nudge_x = 0.1, inherit.aes=FALSE) +
#   scale_color_manual("Shots", values = c("No Shot" = "black", "Give" = "white", "Take" = "red")) +
#   xlab("") + 
#   ylab("") + 
#   coord_cartesian(ylim = c(0, max(beerio_data$Score+3))) +
#   theme_mk8() + 
#   theme(legend.position = "bottom", legend.key = element_rect(fill = "gray70", color = NA)) + 
#   ggtitle("Individual Score Distributions")
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
max_score <- max(table(beerio_data$Score))
median_score <- median(beerio_data$Score, na.rm=T)
mean_score <- mean(beerio_data$Score, na.rm=T)
```

The last plot depicts the overall score distribution with mean (`r round(mean_score,1)`) and median (`r round(median_score,1)`). Green bar sections indicate scores receiving shots.

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=10, fig.align='center', dev="png", dpi = 300}

shift <- ifelse(median_score > mean_score, TRUE, FALSE) 

beerio_data %>%
  ggplot(aes( x = Score)) + 
  geom_bar(fill = "#F8766D", width =1) + 
  ggtitle("Overall Score Distribution") + 
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) + 
  geom_line(data = tibble(x = rep(mean_score, 2),
                          y = c(-.05*max_score, 1.05*max(table(beerio_data$Score)))),
              aes(x = x, y = y), 
            color = "#00BFC4", size = 2) +
  geom_line(data = tibble(x = rep(median_score, 2),
                          y = c(-.05*max_score, 1.05*max(table(beerio_data$Score)))),
            aes(x = x, y = y),
            color = "#C77CFF", size = 2) +
  geom_label(data = tibble(x = c(median_score, mean_score),
                          y = rep(-.06*max_score, 2),
                          label = c("Median", "Mean"),
                          hjust = as.numeric(c(!shift, shift))),
            aes(x=x,y=y,label=label, fill = label, hjust=hjust), size = 4.5, label.size=0, label.padding=unit(0.3,"lines")) +
  scale_fill_manual(values = c(c("Median"="#C77CFF","Mean"="#00BFC4"))) +
  geom_bar(data = beerio_data %>% filter(!is.na(Take)), fill = "#7CAE00", width =1) +
  theme_mk8() +
  ylab("") +
  theme(legend.position = "none", axis.text.y = element_blank())
```

# Round Data

This section depicts the round-level data which contains information on scores in specific maps. Due to difficulty, it may be recorded less frequently than game-level data. The table below shows all recorded rounds.

```{r, include=FALSE}
beerio_rounds_raw <- read_sheet("https://docs.google.com/spreadsheets/d/1V-7lY3NVqVGGEWL-jwwmjYcpLT8mJMN1MI11y-C3Bl0/", sheet = "Round Data")
beerio_rounds <- beerio_rounds_raw %>%
  select(-contains("...")) %>%
  filter_all(any_vars(!is.na(.))) %>%
  fill(Date)

```

```{r, echo=FALSE, message=FALSE}
  
round_table_data <- beerio_rounds %>%
  mutate(Map = fct_recode(Map, 
                          `Luigi's\nMansion`="LM",
                          `Dragon\nPalace`="DP",
                          `Battle\nCourse 1`="BC",
                          `Battle\nStadium`="BS",
                          `Sweet Sweet\nKingdom`="SK",
                          `Wuhu\nTown`="WT",
                          `Urchin\nUnderpass`="UU",
                          `Lunar\nColony`="LC"
                          )) %>%
  mutate(Map = str_replace(as.character(Map), "\n", " ")) %>%
  select(-Korl, -Note) %>%
  mutate(Date = str_replace(format(Date, "%A, %B %e, %Y"), "  ", " ")) 

DT::datatable({
  round_table_data %>% mutate_all(~as.character(.)) %>% select(Date, Game, Round, Map, Chuck, Neil, Shawn, Steve, Shot)
},
callback = JS("
  $.fn.dataTableExt.oSort['NumericOrBlank-asc'] = function(x,y) {
    var retVal;
        if( x === '' || $.isEmptyObject(x)) x = 1000;
    if( y === '' || $.isEmptyObject(y)) y = 1000;
    x = (x = parseFloat($.trim(x).replace(/,/g,''))) ? x : 0;
    y = (y = parseFloat($.trim(y).replace(/,/g,''))) ? y : 0;
    if (x==y) retVal= 0; 
    else retVal = (x>y) ? 1 : -1; 
    return retVal;
  };
  $.fn.dataTableExt.oSort['NumericOrBlank-desc'] = function(y,x) {
  var retVal;
  x = (x = parseFloat($.trim(x).replace(/,/g,''))) ? x : 0;
  y = (y = parseFloat($.trim(y).replace(/,/g,''))) ? y : 0;
  if (x==y) retVal= 0; 
  else retVal = (x>y) ? 1 : -1; 
  return retVal;
  };
  "),
options = list(
  autoWidth = TRUE,
  fillContainer = TRUE,
  pageLength = 10, paging=TRUE, info=TRUE, searching=TRUE, lengthChange=TRUE,
  aoColumnDefs = list(
    list(width = "120px", className = 'dt-center',  targets = c(0)),
    list(width = "40px", className = 'dt-center',  targets = c(1)),
    list(width = '80px',  bSortable = TRUE, sType = 'NumericOrBlank', className = 'dt-center', targets = c(3)),
    list(width = '40px',  bSortable = TRUE, sType = 'NumericOrBlank', className = 'dt-center', targets = c(2,4,5,6,7)),
    list(width = '120px', bSortable = TRUE, sType = 'NumericOrBlank', className = 'dt-center', targets = c(8)))
), escape=FALSE, autoHideNavigation=TRUE, rownames=FALSE, extensions = "Responsive")

```



```{r, include=FALSE}
map_data <- beerio_rounds %>% pivot_longer(Neil:Korl) %>%
  filter(!is.na(name) & !is.na(value)) %>% 
  mutate(Map = fct_recode(Map, 
                          `Luigi's\nMansion`="LM",
                          `Dragon\nPalace`="DP",
                          `Battle\nCourse 1`="BC",
                          `Battle\nStadium`="BS",
                          `Sweet Sweet\nKingdom`="SK",
                          `Wuhu\nTown`="WT",
                          `Urchin\nUnderpass`="UU",
                          `Lunar\nColony`="LC"
                          )) %>%
  mutate(Map = fct_reorder(Map, value, mean)) %>%
  group_by(name, Map) %>% 
  summarize(`Average Score` = mean(value)) %>%
  group_by(Map) %>%
  rename(Player = name)
```

The next table displays average scores for each player on each course.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
map_data_table <- map_data %>% ungroup() %>% mutate(`Average Score` = round(`Average Score`,1 )) %>% pivot_wider(names_from = Player, values_from = `Average Score`) %>% mutate(Map = str_replace(Map, "\n", " "))
DT::datatable({
  map_data_table %>% mutate_all(~as.character(.))
},
callback = JS("
  $.fn.dataTableExt.oSort['NumericOrBlank-asc'] = function(x,y) {
    var retVal;
        if( x === '' || $.isEmptyObject(x)) x = 1000;
    if( y === '' || $.isEmptyObject(y)) y = 1000;
    x = (x = parseFloat($.trim(x).replace(/,/g,''))) ? x : 0;
    y = (y = parseFloat($.trim(y).replace(/,/g,''))) ? y : 0;
    if (x==y) retVal= 0; 
    else retVal = (x>y) ? 1 : -1; 
    return retVal;
  };
  $.fn.dataTableExt.oSort['NumericOrBlank-desc'] = function(y,x) {
  var retVal;
  x = (x = parseFloat($.trim(x).replace(/,/g,''))) ? x : 0;
  y = (y = parseFloat($.trim(y).replace(/,/g,''))) ? y : 0;
  if (x==y) retVal= 0; 
  else retVal = (x>y) ? 1 : -1; 
  return retVal;
  };
  "),
options = list(
  autoWidth = TRUE,
  fillContainer = TRUE,
  pageLength = 8, paging=FALSE, info=FALSE, searching=FALSE, lengthChange=TRUE,
  aoColumnDefs = list(
    list(width = "120px", className = 'dt-center',  targets = c(0)),
    list(width = '45px',  bSortable = TRUE, sType = 'NumericOrBlank', className = 'dt-center', targets = c(1,2,3,4)))), 
  escape=FALSE, autoHideNavigation=TRUE, rownames=FALSE, extensions = "Responsive")
```

The first plot shows the full distribution of scores for each map colored by player. Courses are sorted by their overall mean score--the map with the current highest mean score is `r str_replace(levels(map_data$Map)[8], "\n", " ")`.

```{r, eval=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.width=10, fig.align='center', dev="png", dpi = 300}
# beerio_rounds %>% pivot_longer(Neil:Korl) %>%
#   filter(!is.na(name) & !is.na(value)) %>% 
#   mutate(Map = fct_recode(Map, 
#                           `Luigi's\nMansion`="LM",
#                           `Dragon\nPalace`="DP",
#                           `Battle\nCourse 1`="BC",
#                           `Battle\nStadium`="BS",
#                           `Sweet Sweet\nKingdom`="SK",
#                           `Wuhu\nTown`="WT",
#                           `Urchin\nUnderpass`="UU",
#                           `Lunar\nColony`="LC"
#                           )) %>%
#   mutate(Map = fct_reorder(Map, value, mean)) %>%
#   group_by(name, Map) %>% 
#   summarize(`Average Score` = mean(value)) %>%
#   rename(Player = name) %>%
#   ggplot(aes(x = `Average Score`, y = Map, group = Player, fill = Player)) +
#   facet_grid( 1 ~ Player) +
#   scale_fill_manual("",values = c("Chuck" = "#F8766D", "Neil" = "#7CAE00", "Shawn" = "#00BFC4", "Steve"="#C77CFF")) +
#   scale_x_continuous(breaks = scales::pretty_breaks(3)) +
#   geom_col(position="dodge") + theme_mk8() + theme(legend.position = "none") + ylab("") + ggtitle("Average Scores by Map", subtitle = "For each player")
#   
```


```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=10, fig.height=8.5, fig.align='center', dev="png", dpi = 300}
beerio_rounds %>% pivot_longer(Neil:Korl) %>%
  filter(!is.na(name) & !is.na(value)) %>% 
  mutate(Map = fct_recode(Map, 
                          `Luigi's\nMansion`="LM",
                          `Dragon\nPalace`="DP",
                          `Battle\nCourse 1`="BC",
                          `Battle\nStadium`="BS",
                          `Sweet\nSweet\nKingdom`="SK",
                          `Wuhu\nTown`="WT",
                          `Urchin\nUnderpass`="UU",
                          `Lunar\nColony`="LC"
                          )) %>%
  mutate(Map = fct_rev(fct_reorder(Map, value, mean))) %>%
  rename(Score = value, Player = name) %>%
  count(Map, Player, Score) %>%
  ggplot(aes(x = Score, y = n, fill = Player)) + 
  geom_col() +
  facet_grid( Map ~ ., switch = "y") +
  #geom_violin(show.legend=FALSE, draw_quantiles = c(0.5), legend.show=FALSE) + 
  #geom_point(aes(y = Map, x = Score, fill = Player),  alpha = 0.5, size = 3, 
  #           position = position_jitter(height = 0.1, width=0.1), inherit.aes = FALSE, shape  = 21, color = "black") +
  scale_fill_manual("",values = c("Chuck" = "#F8766D", "Neil" = "#7CAE00", "Shawn" = "#00BFC4", "Steve"="#C77CFF")) +
  xlab("") + 
  ylab("") +
  # scale_y_discrete(limits = rev(c("Chuck", "Neil", "Shawn", "Steve"))) +
  # coord_cartesian(xlim = c(min(beerio_data$Score-3), max(beerio_data$Score+3))) +
  theme_mk8() + 
  geom_hline(yintercept = 0) +
  theme(legend.position = "bottom", axis.text.y = element_blank(), panel.grid = element_blank()) + 
  ggtitle("Map Score Distributions", subtitle = "By player")
```

```{r, include=FALSE}
deviation_data <- map_data %>% group_by(Player) %>% mutate(`Average Score` = `Average Score` - mean(`Average Score`))
neil_ssk <- deviation_data %>% filter(Map=="Sweet Sweet\nKingdom" & Player == "Neil") %>% pull(`Average Score`) %>% round(1)
```

The next plot shows differences between each player's overall average score and their average for the given course. For example, the plot indicates the difference between Neil's overall average and his Sweet Sweet Kingdom average is `r neil_ssk`.

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=10, fig.align='center', dev="png", dpi = 300}
ggplot(deviation_data, aes(x = `Average Score`, y = Map, group = Player, fill = Player)) +
  scale_fill_manual("",values = c("Chuck" = "#F8766D", "Neil" = "#7CAE00", "Shawn" = "#00BFC4", "Steve"="#C77CFF")) +
  geom_col(position="dodge") + theme_mk8() + theme(legend.position = "bottom") + ylab("") + ggtitle("Player Averages by Map", subtitle = "Deviations from player average") +
  scale_x_continuous(breaks = scales::pretty_breaks(3))
```



The last plot provides an alternate visualization of the same information.

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=10, fig.align='center', dev="png", dpi = 300}
beerio_rounds %>% pivot_longer(Neil:Korl) %>%
  filter(!is.na(name) & !is.na(value)) %>% 
  mutate(Map = fct_recode(Map, 
                          `Luigi's\nMansion`="LM",
                          `Dragon\nPalace`="DP",
                          `Battle\nCourse 1`="BC",
                          `Battle\nStadium`="BS",
                          `Sweet Sweet\nKingdom`="SK",
                          `Wuhu\nTown`="WT",
                          `Urchin\nUnderpass`="UU",
                          `Lunar\nColony`="LC"
                          )) %>%
  mutate(Map = fct_reorder(Map, value, mean)) %>%
  group_by(name, Map) %>% 
  summarize(`Average Score` = mean(value)) %>%
  rename(Player = name) %>%
  group_by(Player) %>%
  mutate(`Average Score` = `Average Score` - mean(`Average Score`)) %>%
  ggplot(aes(x = `Average Score`, y = Map, group = Player, fill = Player)) +
  facet_grid(1 ~ Player) +
  scale_fill_manual("",values = c("Chuck" = "#F8766D", "Neil" = "#7CAE00", "Shawn" = "#00BFC4", "Steve"="#C77CFF")) +
  scale_x_continuous(breaks = scales::pretty_breaks(3)) +
  geom_col(position="dodge") + theme_mk8() + theme(legend.position = "none") + ylab("") + ggtitle("Player Average by Map", subtitle = "Deviations from player average")
```

